\section{Objective}

\comment{Vom Blatt}

\textbf{}

\subsection{Mandatory Criterias}

\begin{itemize}
  \item Comm sensor/app
  \item Sensordaten visualisierung (mehr als eine)
  \item Exploration (mit Joystick)
  \item Comm app/webVR/sensor(als Beacon)
  \item Positionapproximation durch beacons

  \item VR-Mode
  \begin{itemize}
    \item The VR-World shall model at least two different rooms and a connect hallway.
    \item The VR-World shall be viewed inside a web browser and from the App.
    \item The VR-World shall have a stereoscopic 3D-Mode of the World.
    \item While viewing the VR-World the user shall be able to look around using the gyro senor of his phone to pan the camera around.
    \item While the App is not in stereoscopic 3D mode the User shall be able to click and drag to pan the camera around.
    \item The User shall be able to move the camera inside the Vr-World by using his controller.
    \item The Data fechted from the Sensor shall be displayed inside the VR-World.
    \item There shall be at least two different representations the data from the Sensor.
    \item The VR-World shall represent at least two different real world rooms.
    \item The User shall be able to easily switch between stereoscopic 3D and normal 3D mode.
    \item The App shall be in fullscreen mode, while in VR-Mode.
    \item While in stereoscopic 3D-Mode the user shall be able to exit it by looking for 5 seconds at the cross under his feet.
  \end{itemize}
  \item Other
  \begin{itemize}
    \item The App shall not dimm the screen while inside VR-Mode.
    \item
  \end{itemize}
\end{itemize}

\subsection{Desired Criterias}

\begin{itemize}
  \item The VR-World represents a whole corridor with more then two rooms.
  \item AR
  \item TI sensor als bewegung
\end{itemize}

\subsection{Boundary Criterias}

\begin{itemize}
  \item Keine persistente Speicherung
\end{itemize}
