\section{Product Functions}

%\comment{functional Requirements}

\subsection{General Features}
\begin{description}
  \item[F1.1] The app shall use the Bluetooth adapter of the smartphone and the Android.bluetooth library to connect to a TI SimpleLink SensorTag device.
  \item[F1.2] The app shall provide a live data view of the sensor feedback in human readable form.
  \item[F1.3] The app shall track connected TI SimpleLink SensorTag devices.
\end{description}

\subsection{VR-World}
  The VR-Mode is a 3D view of the world. When entering VR-Mode the user will see a fullscreen 3D world and by pressing the button in the lower right corner he can enter the  stereoscopic view of the World.
  The VR-World is a 3D representation of a real series of rooms.
  \begin{description}
    \item[F2.1] The VR-World shall be able to be viewed inside a web browser and from within the app.
    \item[F2.2] While viewing the VR-World the user shall be able to look around using the gyro sensor of his phone to pan the camera around.
    \item[F2.3] While the app is not in stereoscopic 3D mode the user shall be able to click and drag to pan the camera around.
    \item[F2.4] The app shall be able to move the camera inside the VR-World by using a bluetooth controller.
    \item[F2.5] The data fechted from the sensors shall be displayed inside the VR-World.
    \item[F2.6] When in VR-Mode, the app shall be in fullscreen mode.
    \item[F2.7] The app shall exit the VR-Mode if the user is pressing the ``x'' in the top right corner of the screen or if the user is looking directly at the ``x'' under his feet for 5 seconds .
    \item[F2.8] The app shall be able to switch between stereoscopic 3D and normal 3D mode.
    \item[F2.9] The app shall be able to switch from fullscreen VR-Mode to stereoscopic by pressing the button in the lower right corner or by pressing the A-Button on his controller.
    \item[F2.10] The app shall be able to exit the stereoscopic 3D mode by the user looking at the ``x'' under his feet for 5 seconds or by pressing the back button on his device or by touching the back button in the top left corner.
    \item[F2.11] The app shall be able to switch to the settings screen, while it's in normal 3D mode.
    \item[F2.12] The app shall be able to switch rooms if the user pushes the B-Button on his controller or by looking up at the door sign for at least 5 seconds when the app is in a visualization state.
    \item[F2.13] The app shall visualize the position of connected TI SimpleLink SensorTag devices.
    \item[F2.14] The app shall visualize the temperature given by the Ti SimpleLink SensorTag, by displaying a graph at the sensors location.
    \item[F2.15] The app shall visualize the temperature by showing a glowing sphere at the location of the sensor, which will become more red the hotter the room gets,
                while in this representation there will be scale in the top left corner of the hud.
    \item[F2.16] The User shall be able to switch between the two representation by pressing the b button on his controller.
  \end{description}



  \subsection{Settings}
    The user can set the following options:

    \begin{description}
      \item[F3.1] The app shall be configuarable so that the user may choose wich data shall be displayed in the VR-World (temperature, etc.).
      \item[F3.2] The app shall list the connected devices and a short info about the current setting and state of the TI SimpleLink SensorTag device.
      \item[F3.4] The app shall list the results of a Bluetooth scan and present an user interface for controlling the connection of TI SimpleLink SensorTag devices.
    \end{description}
